Towards a self-healing swarm through the removal of voids and anomalies

### 2018-10-08 paper.tex
Swarm Model
Abstract Intro and Method

\section{Swarm Model}\label{sec:Swarm Model}
To describe the removal of voids a swarming algorithm needs to be defined. Equation~\ref{eq:BotPhysics1} defines a weighted algorithm that includes cohesion, repulsion, direction and obstacle avoidance ($v_c(b), v_r(b), v_d(b), v_o(b)$). The weightings $k_c, k_r, k_d, k_o$ allow each component to be scaled thereby creating an adaptable swarming effect.

@@

\textit{Repulsion} $v_{r}(b)$, as defined in Equation~\ref{eq:Repulsion1} is the resultant directional movement required to prevent agents colliding.

@@

\textit{Cohesion} $v_{c}(b)$, as defined in Equation~\ref{eq:FlyToCentre1} is the resultant movement that makes the agent move towards each other to form a cohesive structure.

@@

Obstacles, like agents, can be represented as a point in the system. As an agent moves it may enter an obstacle's \textit{obstacle repulsion field} ($O_b$) causing the agent to move away. In this paper agents are modelled with a fixed \textit{obstacle repulsion field} ($O_b$). If an agent enters the field range a vector of magnitude $O_b$ is applied. If more than one obstacle is within the field effect the applied repulsion vector is the sum of the repulsion vectors due to each obstacle~Figure~\ref{methods:Obstacle1}. The result is normalised and scaled such that the magnitude is the same as the field distance~$O_b$ as shown in Equation~\ref{eq:Obstacle2}.

\begin{figure}[H]
\begin{center}
\includegraphics[width=6cm]{figures/Obstacle1}
\end{center}
\caption{Obstacle repulsion \label{methods:Obstacle1}}
\end{figure}

>>>>

\section{Swarm Model}\label{sec:Swarm Model}
To describe the removal of voids a swarming model needs to be defined. Equation~\ref{eq:BotPhysics1} defines a weighted algorithm that includes cohesion, repulsion, direction and obstacle avoidance ($v_c(b), v_r(b), v_d(b), v_o(b)$). The weightings $k_c, k_r, k_d, k_o$ allow each component to be scaled thereby creating an adaptable swarming effect.

@@

\textit{Repulsion} $v_{r}(b)$, as defined in Equation~\ref{eq:Repulsion1} is the resultant directional movement required to prevent agents colliding where $rep(b)$ is a function that returns a set of agents that are within the agent $b$ repulsion range.

@@

\textit{Cohesion} $v_{c}(b)$, as defined in Equation~\ref{eq:FlyToCentre1} is the resultant movement that makes the agent move towards each other to form a cohesive structure where $nbr(b)$ is a function that returns set of all agents that are within agent $b$ cohesion range.

@@

Obstacles, like agents, can be represented as a point in the system. As an agent moves it may enter an obstacle's \textit{obstacle repulsion field} ($O_b$) causing the agent to move away. In this paper agents are modelled with a fixed \textit{obstacle repulsion field} ($O_b$). If an agent enters the field range a vector of magnitude $O_b$ is applied. If more than one obstacle is within the field effect, the applied repulsion vector is the sum of the repulsion vectors due to each obstacle~(Figure~\ref{fig:Obstacle1}). The result is normalised and scaled such that the magnitude is the same as the field distance~$O_b$ as shown in Equation~\ref{eq:Obstacle2}.

\begin{figure}[H]
\begin{center}
\includegraphics[width=6cm]{figures/Obstacle1}
\end{center}
\caption{Obstacle repulsion \label{fig:Obstacle1}}
\end{figure}
